Would NEMO benefit from using the \psyclone\ system?

### 2017-01-11 docs/NEMO/psyclone_and_nemo.tex
Break up introduction into two sections and update the reference to the Shallow paper

In the GOcean2D project we investigated the use of the \psykal\ and
\psyclone\ approach for models using a finite-difference scheme on a
regular lat-lon grid. For this work we took two different
shallow-water models, one of which was the 2D, free-surface component
of NEMO. After restructuring these programs according to the
\psykal\ separation of concerns we were able to show that the
performance of the original code could be recovered with optimisations
restricted to the PSy layer. We also demonstrated that this code could
run efficiently on multi-core architectures using OpenMP directives
and GPU architectures using OpenACC, again with optimisations
restricted to the PSy layer.

The question now is, would this approach be valuable and applicable
for the full NEMO code?  Key to this is the fact that the full NEMO
code is a combination of both 3D and 2D components and thus we have to
decide how the loop over levels (the ``k-loop'') might fit within the
\psyclone\ framework. In Dynamo this loop over levels is not managed by
\psyclone\ but instead is performed within each kernel as a way of
amortising the cost of the indirection associated with the
unstructured mesh.

@@

\bibitem{psykal_shallow} A.~R.~Porter, R.~W.~Ford, M.~Ashworth, G.~D.~Riley and M.~Modani, ``Towards Compiler-Agnostic Performance in Finite-Difference Codes'', to appear in the Proceedings of ParCo 2015.

>>>>

In the GOcean2D project we investigated the use of the \psykal\ and
\psyclone\ approach for models using a finite-difference scheme on a
regular lat-lon grid. For this work we took two different
shallow-water models, one of which was the 2D, free-surface component
of NEMO. After restructuring these programs according to the
\psykal\ separation of concerns we were able to show that the
performance of the original code could be recovered with optimisations
restricted to the PSy layer.\cite{psykal_shallow} We also demonstrated
that this code could run efficiently on multi-core architectures using
OpenMP directives and GPU architectures using OpenACC, again with
optimisations restricted to the PSy layer.

The question now is, would this approach be valuable and applicable
for the full NEMO code? We expand on this in the rest of this document.

\section{Managing the Iteration Space}

In contrast to the codes tackled in GOcean, the full NEMO code
contains a combination of both 3D and 2D components and thus we have
to decide how the loop over levels (the ``k-loop'') might fit within
the \psyclone\ framework. In Dynamo this loop over levels is not
managed by \psyclone\ but instead is performed within each kernel as a
way of amortising the cost of the indirection associated with the
unstructured mesh.

@@

\bibitem{psykal_shallow} A.~R.~Porter, R.~W.~Ford, M.~Ashworth, G.~D.~Riley and M.~Modani, ``Towards Compiler-Agnostic Performance in Finite-Difference Codes'', in ``Parallel Computing: On the Road to Exascale'', editors Gerhard R. Joubert and Hugh Leather and Mark Parsons and Frans Peters and Mark Sawyer, 27, 647-658 (2016) IOS Press, (Amsterdam, New York, Tokyo)
